---
title: "COVID_Quarantine"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{COVID_Quarantine}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CovidDataPackage1)
```
## Overview

The **COVID-19 Outbreak Risk Explorer** is an interactive Shiny application included within the `CovidDataPackage1` package.  
It allows users to explore how different factors such as vaccination rates, vaccine efficacy, testing frequency, and viral transmissibility (R₀) influence the overall probability of a COVID-19 outbreak under different variant scenarios.

This app provides an interactive visual environment to replicate and extend the findings from the accompanying dataset `covid_data`, which is stored within the package. The dataset contains simulated information on key public-health parameters and their relationships to outbreak risk.

---

## Data Description

The dataset `covid_data` includes the following variables:

| Variable | Description |
|-----------|--------------|
| `variant` | The COVID-19 variant (e.g., Wildtype, Delta, Omicron). |
| `vaccination_rate` | Proportion of the population vaccinated. |
| `vaccine_efficacy` | Effectiveness of the vaccine in preventing infection. |
| `testing_freq_days` | Average number of days between population testing. |
| `R0` | Basic reproduction number — the average number of secondary infections caused by one infected person. |
| `outbreak_risk` | Simulated probability of an outbreak occurring under the specified conditions. |

These variables can be explored interactively in the Shiny app to observe how changes in vaccination or testing policies might affect outbreak potential.

---


